Magnetised Polish doughnuts revisited

### 2017-07-04 paper_revised/paper_revised.tex
some typos corrected

Moreover, we can use Eqs.~\eqref{eq:eos_fluid}, \eqref{eq:eos_mag} and \eqref{eq:beta_eq} at the center (remember that $w_{\mathrm{c}} = 1$) to write $K$ as $K = \beta_{\mathrm{m}_{\mathrm{c}}} K_\mathrm{m}\mathcal{L}^{\lambda -1}$. Therefore, this allows us to obtain the following simple expression for the value of the magnetisation parameter at the center of the disc

>>>>

Moreover, we can use Eqs.~\eqref{eq:eos_fluid}, \eqref{eq:eos_mag} and \eqref{eq:beta_eq} at the centre (remember that $w_{\mathrm{c}} = 1$) to write $K$ as $K = \beta_{\mathrm{m}_{\mathrm{c}}} K_\mathrm{m}\mathcal{L}^{\lambda -1}$. Therefore, this allows us to obtain the following simple expression for the value of the magnetisation parameter at the centre of the disc
